---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sourrr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sourrr)](https://CRAN.R-project.org/package=sourrr)
<!-- badges: end -->

Use {sourrr} to generate sourdough bread recipes using [baker's percentages](https://www.theperfectloaf.com/reference/introduction-to-bakers-percentages/).

## Installation

You can install the development version of {sourrr} from github with:

``` r
# install.packages("remotes")
remotes::install_github("andrewheiss/sourrr")
```

## Example

Suppose you want to bake a 75% hydration loaf that weighs 900 grams using 100% hydration sourdough starter (i.e. you feed it a 1:1 ratio of flour and water). Use the `build_recipe()` function to generate the appropriate recipe:

```{r}
library(sourrr)
build_recipe(final_weight = 900, hydration = 0.75)
```

You can set all the arguments:

```{r}
build_recipe(final_weight = 900, hydration = 0.90,
             pct_starter = 0.25, starter_hydration = 1,
             pct_salt = 0.02)
```

For now, it's not 100% correct because I add the salt to the final loaf weight. The math is too tricky and I can't figure it out right now with, like, the ongoing global pandemic :shrug:.

If you have an existing recipe, you can use the `calculate_recipe()` function to determine the hydration level:

```{r}
calculate_recipe(flour = 450, water = 320,
                 starter = 100, starter_hydration = 1, salt = 8)
```
